Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-08 ms.tex
writing about attempts to fix reddening residuals

@@

The obvious culprit for any potential nonlinearity in FIR-based reddening
estimates is a faulty temperature correction. For this reason, we have included
the bottom panels of Figure \ref{fig:resid}, to check for the presence of
a dependence of the reddening residuals on dust temperature.

%Clearly there are some systematic trends in the residuals.
%Still, for $E(B-V)_{SFD}$$<$0.28 ($\sim$80\% of the sky), the residual median 
%is always within 10 mmag of zero. Over the entire range $E(B-V)_{SFD}$$<$0.7, 
%the residual median is always within 30 mmag of zero.

\subsection{Rectifying Reddening Residuals}
% discuss changing global params and offsets, and ecl plane cut

>>>>

% MENTION THAT THE TAU TEMPLATE IS INDEPENDENT OF FREQUENCY FOR 
% TWO-COMPONENT MODELS WITH SPATIALLY CONSTANT BETAS, Q1/Q2 AND F1

@@

% could add a sentence praising the two-component reddening prediction for
% only having issues at the ~<10 mmag level for EBV_SFD ~< 0.4 mag, since
% it could be a lot worse ...

The obvious culprit for any potential nonlinearity in FIR-based reddening
estimates is a faulty temperature correction. For this reason, we have included
the bottom panels of Figure \ref{fig:resid}, to check for the presence of
a temperature dependence of the reddening residuals. Indeed, in both the
two-component and single-MBB cases there exists some systematic dependence of
the reddening residuals on temperature. For $T_{mbb}$$\gtrsim$19 K, the 
median residual is reasonably flat, but at lower temperatures (the lowest 
temperature $\sim$20\% of the sky), the median shows trends at the $\sim$10 
mmag level. On the other hand, the median residual in the two-component case 
shows a clear trend of decreasing with increasing $T_2$ over the entire range
of $T_2$ shown, with a peak-to-peak amplitude of $\sim$20 mmag.

\subsection{Rectifying Reddening Residuals}
In this section we describe our attempts to eliminate the systematic
problems in the two-component reddening residuals shown in the left column
of Figure \ref{fig:resid}. We employed two main strategies: (1) recompute
the two-component $\tau_{545}$ by re-running our Markov chains after modifying 
the input maps and/or changing the particular two-component model adopted and
(2) making spatial cuts to isolate sky regions in which the 
residuals are especially pristine (or especially problematic).

The following is a list of dust model modifications we tested, but 
proved to have little impact on the shape of the reddening residuals versus
$E(B-V)_{SFD}$ and $T_2$:

\begin{itemize}
\item Varying each of the global two-component model parameters $\beta_1$, 
$\beta_2$, $q_1/q_2$ and $f_1$ individually while holding the others fixed.
\vspace{-3mm}
\item Allowing $f_1$ to vary spatially as in the fits of $\S$\ref{sec:lores}.
\vspace{-2mm}
\item Changing the mean and/or variance of the $T_2$ prior.
\vspace{-6mm}
\item Varying multiple global parameters at a time e.g. both $f_1$ and 
$q_1/q_2$, restricting to regions of parameter space favored by our 
goodness-of-fit analyses described in $\S$\ref{sec:global} and 
$\S$\ref{sec:hier}.
\end{itemize}

We additionally investigated spatial cuts which did not resolve the 
dominant problems noted in the reddening residuals:

% discuss changing global params and offsets, and ecl plane cut
